\section*{Euler's Method}

\begin{enumerate}

\item What problem does Euler's method aim to solve? State the general form of an initial value problem.

\item What is the geometric interpretation of Euler's method in terms of tangent lines?

\item Starting from the differential equation $y'(x) = f(x,y)$, derive the Euler update formula.

\item Write the recursive formula for Euler's method, defining all variables involved.

\item What role does the step size $h$ play in Euler's method?

\item Given an initial condition $y(x_0) = y_0$, how do you compute $y_1$ using Euler's method?

\item How do you compute $y_{n+1}$ from $y_n$ in Euler's method?

\item What is meant by a numerical approximation to a solution of an ODE?

\item What is the local truncation error in Euler's method?

\item What is the global truncation error in Euler's method?

\item What is the order of accuracy of Euler's method?

\item How does decreasing the step size $h$ affect the accuracy of Euler's method?

\item What is the trade-off between accuracy and computational cost in Euler's method?

\item Apply Euler's method with step size $h = 0.1$ to approximate the solution of $y' = y$, $y(0) = 1$ at $x = 0.1$.

\item Apply Euler's method for two steps to approximate the solution of $y' = x + y$, $y(0) = 1$, with $h = 0.5$.

\item What types of errors can accumulate in Euler's method over many steps?

\item What is meant by stability in the context of numerical methods for ODEs?

\item Why can Euler's method become unstable for certain differential equations?

\item Give an example of a differential equation where Euler's method performs poorly.

\item What is the difference between explicit Euler and implicit Euler methods?

\item Write the update formula for the implicit Euler method.

\item What advantage does the implicit Euler method have over the explicit version?

\item What is a stiff differential equation, and why is Euler's method problematic for such equations?

\item How can you modify Euler's method to improve accuracy (e.g., midpoint or improved Euler methods)?

\item What is the idea behind the Heun method (improved Euler method)?

\item Compare Euler's method with higher-order methods like Runge--Kutta methods.

\item Why is Euler's method rarely used in practice for high-precision computations?

\item How can you estimate the error in Euler's method during computation?

\item What happens if the function $f(x,y)$ is not smooth? How does this affect Euler's method?

\item In what situations might Euler's method still be useful despite its limitations?

\item How would you implement Euler's method algorithmically?

\item Write pseudocode for Euler's method.

\item How does Euler's method relate to the Taylor series expansion of the solution?

\item What term(s) of the Taylor series does Euler's method include or neglect?

\item Can Euler's method be used for systems of differential equations? How?

\item How does Euler's method behave when applied backward in time (negative step size)?

\item What are common pitfalls when using Euler's method in practice?

\item How would you visualize the steps of Euler's method on a slope field?

\item What is the difference between consistency, stability, and convergence in the context of Euler's method?

\item State the relationship between consistency, stability, and convergence (Lax equivalence theorem).

\end{enumerate}
