\section*{The Gamma Function}

\begin{enumerate}

\item What is the definition of the Gamma function $\Gamma(x)$ for $x > 0$?

\item For which values of $x$ is the integral definition of $\Gamma(x)$ valid?

\item Show that $\Gamma(1) = 1$.

\item Prove the functional equation $\Gamma(x+1) = x\Gamma(x)$.

\item How does the Gamma function extend the factorial function? State the relationship between $\Gamma(n)$ and $(n-1)!$ for $n \in \mathbb{N}$.

\item Compute $\Gamma(2)$, $\Gamma(3)$, and $\Gamma(4)$ using the functional equation.

\item What is the value of $\Gamma\left(\tfrac{1}{2}\right)$?

\item How can the integral $\int_0^\infty e^{-t^2},dt$ be used to compute $\Gamma\left(\tfrac{1}{2}\right)$?

\item What substitution transforms the Gaussian integral into the Gamma function integral?

\item What is the reflection formula for the Gamma function?

\item Use the reflection formula to compute $\Gamma\left(\tfrac{1}{2}\right)$.

\item What is the duplication formula (Legendre's formula) for the Gamma function?

\item What is the behavior of $\Gamma(x)$ near $x = 0$?

\item Does the Gamma function have any poles? If so, where are they located?

\item Is the Gamma function defined for negative non-integer values? What happens at negative integers?

\item What is the logarithmic derivative of the Gamma function called?

\item Define the digamma function $\psi(x)$.

\item What is the integral representation of $\Gamma(x)$ involving $e^{-t} t^{x-1}$?

\item What is an alternative integral representation of $\Gamma(x)$ using a limit (Euler's limit form)?

\item What is Stirling's approximation for $\Gamma(x)$ for large $x$?

\item How can Stirling's formula be used to approximate $n!$?

\item What is the Beta function $B(x,y)$?

\item How is the Beta function related to the Gamma function?

\item Show that $B(x,y) = \dfrac{\Gamma(x)\Gamma(y)}{\Gamma(x+y)}$.

\item What is the integral definition of the Beta function?

\item How can you derive the Beta-Gamma relationship using a change of variables?

\item What is the asymptotic growth rate of $\Gamma(x)$ as $x \to \infty$?

\item Is the Gamma function convex or concave on $(0,\infty)$?

\item What is the logarithmic convexity (log-convexity) property of $\Gamma(x)$?

\item State Bohr–Mollerup theorem and explain its significance.

\item How does the Gamma function behave under scaling transformations?

\item What is the value of $\Gamma\left(\tfrac{3}{2}\right)$?

\item Compute $\Gamma\left(\tfrac{5}{2}\right)$ using recursion.

\item Express $\Gamma\left(n+\tfrac{1}{2}\right)$ in terms of factorials and $\sqrt{\pi}$.

\item What is the relation between $\Gamma(x)$ and improper integrals in probability theory?

\item How does the Gamma function appear in the definition of the Gamma distribution?

\item What is the probability density function of the Gamma distribution?

\item What role does $\Gamma(x)$ play in normalizing probability distributions?

\item How can $\Gamma(x)$ be analytically continued to complex numbers?

\item Is $\Gamma(x)$ an entire function? Why or why not?

\item Where are the zeros of the Gamma function located?

\item What is the Weierstrass product representation of $\Gamma(x)$?

\item How does $\Gamma(x)$ relate to complex analysis and contour integrals?

\item What is Euler's constant $\gamma$ and how does it relate to $\Gamma(x)$?

\item What is the series expansion of $\log \Gamma(x)$ near $x=1$?

\item How is the Gamma function used in evaluating definite integrals?

\item Give an example of an integral that evaluates to a Gamma function.

\item How does the substitution $t = -\ln u$ relate the Gamma function to integrals over $(0,1)$?

\item What is the connection between $\Gamma(x)$ and factorial moments?

\item Why is the Gamma function important in physics and engineering?

\end{enumerate}
