\section*{Derivative of the Inverse Function}

\begin{enumerate}

\item What is the definition of the inverse of a function $f$? Under what condition does an inverse exist?

\item What does it mean for a function to be one-to-one (injective), and why is this property necessary for the existence of an inverse?

\item State the relationship between a function and its inverse using composition.

\item If $y = f(x)$, how do you express $x$ in terms of $f^{-1}$?

\item What is the geometric relationship between the graphs of $f$ and $f^{-1}$?

\item How can you determine whether a function has an inverse using the horizontal line test?

\item State the formula for the derivative of an inverse function: \[ (f^{-1})'(x) = ? \]

\item Derive the formula for $\left(f^{-1}\right)'(x)$ starting from the identity $f(f^{-1}(x)) = x$.

\item If $f(a) = b$, express $\left(f^{-1}\right)'(b)$ in terms of $f'(a)$.

\item Under what conditions on $f$ does the derivative of the inverse function exist?

\item Why must $f'(a) \neq 0$ for the inverse function to be differentiable at $b = f(a)$?

\item Compute $\left(f^{-1}\right)'(x)$ when $f(x) = x^3 + x$.

\item Let $f(x) = \sin x$ restricted to $\left[-\frac{\pi}{2}, \frac{\pi}{2}\right]$. What is $f^{-1}(x)$ and its derivative?

\item Find the derivative of $\arctan(x)$ using the inverse function derivative formula.

\item Show that the derivative of $\ln x$ can be derived from the inverse of $e^x$.

\item If $f'(x)$ is known, describe the steps to compute $\left(f^{-1}\right)'(x)$ at a specific point.

\item What happens to $\left(f^{-1}\right)'(x)$ if $f'(x)$ is very large? What is the geometric interpretation?

\item What happens to $\left(f^{-1}\right)'(x)$ if $f'(x)$ is very small (but nonzero)?

\item Explain why the slopes of inverse functions at corresponding points are reciprocals.

\item If $f$ is decreasing and invertible, what can you say about the sign of $\left(f^{-1}\right)'(x)$?

\item Let $f(x) = x^5$. Compute $\left(f^{-1}\right)'(x)$ explicitly.

\item If $f(x) = \tan x$ on $\left(-\frac{\pi}{2}, \frac{\pi}{2}\right)$, compute the derivative of its inverse.

\item Verify that $\frac{d}{dx}(\arcsin x) = \frac{1}{\sqrt{1 - x^2}}$ using the inverse function rule.

\item How does implicit differentiation relate to finding the derivative of an inverse function?

\item If $f$ is differentiable and strictly monotonic on an interval, what can be said about the differentiability of $f^{-1}$?

\item Give an example of a function that is invertible but whose inverse is not differentiable at some point.

\item What is the domain of $f^{-1}$ in terms of the range of $f$?

\item What is the range of $f^{-1}$ in terms of the domain of $f$?

\item How can you use the inverse function derivative formula to avoid explicitly finding the inverse?

\item Let $f(2) = 5$ and $f'(2) = 3$. Find $\left(f^{-1}\right)'(5)$.

\end{enumerate}
