\section*{Roots of Unity}

\begin{enumerate}

\item What is meant by an $n$th root of unity?

\item Write the equation whose solutions are the $n$th roots of unity.

\item How many distinct $n$th roots of unity are there? Why?

\item Express the $n$th roots of unity in exponential form using Euler's formula.

\item Write the general formula for the $k$th $n$th root of unity.

\item What is the principal (or primitive) $n$th root of unity?

\item How can all $n$th roots of unity be generated from a single primitive root?

\item What is the difference between a root of unity and a primitive root of unity?

\item State the condition under which a root of unity is primitive.

\item How many primitive $n$th roots of unity are there? Which function counts them?

\item What is Euler's totient function $\varphi(n)$ and how does it relate to roots of unity?

\item Represent the $n$th roots of unity geometrically in the complex plane.

\item What is the magnitude and argument of each $n$th root of unity?

\item How are the $n$th roots of unity distributed on the complex unit circle?

\item What is the angle between consecutive $n$th roots of unity?

\item Compute the sum of all $n$th roots of unity. What is the result?

\item Why does the sum of all $n$th roots of unity equal zero?

\item Compute the product of all $n$th roots of unity.

\item What symmetry properties do the $n$th roots of unity exhibit?

\item Show that the $n$th roots of unity form a group under multiplication.

\item What type of group is formed by the $n$th roots of unity?

\item What is the identity element in this group?

\item What is the inverse of a given $n$th root of unity?

\item Show that the set of $n$th roots of unity is cyclic.

\item What is a generator of the group of $n$th roots of unity?

\item For which values of $k$ is $\zeta^k$ a primitive root, where $\zeta$ is a primitive $n$th root?

\item Solve the equation $z^n = 1$ explicitly for small values such as $n=2,3,4$.

\item What are the cube roots of unity? Write them explicitly.

\item What are the fourth roots of unity? Write them explicitly.

\item How can roots of unity be used to factor the polynomial $x^n - 1$?

\item Write the factorization of $x^n - 1$ in terms of its complex roots.

\item What are cyclotomic polynomials and how are they related to roots of unity?

\item Define the $n$th cyclotomic polynomial $\Phi_n(x)$.

\item How does $x^n - 1$ factor into cyclotomic polynomials?

\item What is the relationship between primitive roots of unity and cyclotomic polynomials?

\item How can roots of unity be used to evaluate sums such as $\sum_{k=0}^{n-1} \zeta^{k}$?

\item Evaluate $\sum_{k=0}^{n-1} \zeta^{mk}$ for an integer $m$.

\item Under what condition does $\sum_{k=0}^{n-1} \zeta^{mk} = 0$?

\item What happens when $m$ is a multiple of $n$ in the above sum?

\item How are roots of unity used in discrete Fourier transforms (DFT)?

\item What is the connection between roots of unity and periodicity?

\item How can roots of unity simplify computations involving periodic sums?

\item Show that if $\zeta$ is an $n$th root of unity, then $\overline{\zeta} = \zeta^{-1}$.

\item What is the complex conjugate of a root of unity geometrically?

\item How do roots of unity relate to rotations in the complex plane?

\item What is the minimal polynomial of a primitive $n$th root of unity?

\item How does the degree of $\Phi_n(x)$ relate to $\varphi(n)$?

\item In what fields do primitive $n$th roots of unity lie?

\item What is the significance of roots of unity in number theory?

\item How are roots of unity used in solving polynomial equations?

\end{enumerate}
