\section{Tangent Planes}

\begin{enumerate}
  \item Compare the tangent line in single-variable calculus with the tangent plane in multivariable calculus.
  \item What is the definition of a tangent plane to a surface $z = f(x,y)$ at a point $(x_0, y_0)$?
  \item How do the partial derivatives $\frac{\partial f}{\partial x}$ and $\frac{\partial f}{\partial y}$ relate to the slope of the tangent plane?
  \item Compute the tangent plane to $f(x,y) = x^2 + y^2$ at the point $(1,2)$.
  \item What is the geometric meaning of the linear approximation
    \[
      L(x,y) = f(x_0,y_0) + f_x(x_0,y_0)(x - x_0) + f_y(x_0,y_0)(y - y_0)?
    \]
  \item How is the tangent plane related to the total derivative of $f(x,y)$?
  \item Explain how the gradient vector $\nabla f(x_0,y_0)$ is connected to the tangent plane.
  \item For a surface given implicitly by $F(x,y,z)=0$, how do you find the equation of the tangent plane at a point?
  \item What role does the gradient $\nabla F(x_0,y_0,z_0)$ play in the implicit surface case?
  \item Compute the tangent plane to the surface $x^2 + y^2 + z^2 = 9$ at the point $(1,2,2)$.
  \item What is the normal vector to the tangent plane of $z = f(x,y)$?
  \item How can you express the tangent plane using a normal vector and a point?
  \item What is the relationship between the tangent plane and directional derivatives?
  \item How can you use the tangent plane to approximate the value of a function near a point?
  \item Under what circumstances might a function fail to have a tangent plane at a point?
  \item Given a parameterized surface $\mathbf{r}(u,v)$, how do you compute the tangent plane at a point?
  \item What vectors span the tangent plane in the parameterized surface case?
  \item Compute the tangent plane to the parameterized surface $\mathbf{r}(u,v) = (u, v, u^2 + v^2)$ at $(1,1,2)$.
  \item How is the cross product used in finding the normal vector to a parameterized surface?
  \item What is the difference between a tangent plane and a secant plane?
  \item How does the tangent plane behave near critical points where $\nabla f = 0$?
  \item Why is the tangent plane considered the best linear approximation of a surface near a point?
\end{enumerate}
